Ice sheet mass flows

### 2024-05-24 ms.tex
AQ BMB from pattyn_2010
Addresses #14.

>>>>

\section{Methods}

Use published values

Approximate where values are not easily accessed.

We do not have access to the basal mass balance for Antarctica in spatial map form, only a total Antarctic-wide value from \citet{pattyn_2010}. To estimate basal melt for East and West Antarctica, we scale by the approximate areas of East and West Antarctica, or 75 \% and 25 \% respectively.
